\bf An observational study of papers published in \emph{PLOS ONE} and studies posted to a trial registry.

### 2021-05-25 manuscript/asa_template/asa_template_almostdone.tex
update manuscript plos results

For studies excluded based on section headings, initial search terms
appeared in Introduction (number), Results (number) only. xxx appeared
in the Methods section without a section heading and xxx had a
non-standard section heading. {[}TODO{]}.

>>>>

For studies excluded based on section headings (n = 20,116), 2,136 DOIs included search terms as part of the Materials and Methods section. For studies without a matching Materials and Methods section,
 search terms oftern featured in the Introdction (n = 728) and Results and/or Discussion (n = 981) sections. 4,010 DOIs included at least 1 heading that included the terms ``analysis'' or ``analyses'' without direct reference to statistical method(s) (e.g. Microarray analysis).
